---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/hypertidy/svgplotr.svg)](https://travis-ci.org/hypertidy/svgplotr) 
[![codecov](https://codecov.io/gh/hypertidy/svgplotr/branch/master/graph/badge.svg)](https://codecov.io/gh/hypertidy/svgplotr)
[![Project Status: Concept - Minimal or no implementation has been done yet.](http://www.repostatus.org/badges/0.1.0/concept.svg)](http://www.repostatus.org/#concept)

# svgplotr

Fast `svg` plots in **R**. Currently just a demonstration of speed relative to
[`svglite`](https://github.com/r-lib/svglite) based on four functions:

1. `getlines(n)` which generates a series of `n` random edges tracing a single
   path with varying colours and line widths;
2. `getpoints(n)` which generates `n` random points with varying colours;
3. `svgplot_lines()` to write line data to a `html`-formatted `svg` file.
4. `svgplot_points()` to write point data to a `html`-formatted `svg` file.

Comparison is against a `ggplot2` object with no embellishments, set up with the
following code
```{r load, echo = FALSE, message = FALSE}
devtools::load_all (".", export_all = FALSE)
```
```{r ggplot-setup, message = FALSE}
require (ggplot2)
ggmin_theme <- function ()
{
    theme <- theme_minimal ()
    theme$panel.background <- element_rect (fill = "transparent",
                                                     size = 0)
    theme$line <- element_blank ()
    theme$axis.text <- element_blank ()
    theme$axis.title <- element_blank ()
    theme$plot.margin <- margin (rep (unit (0, 'null'), 4))
    theme$legend.position <- 'none'
    theme$axis.ticks.length <- unit (0, 'null')
    return (theme)
}
ggline <- function (dat)
{
    ggplot () + ggmin_theme () +
        geom_segment (aes (x = xfr, y = yfr, xend = xto, yend = yto, size = lwd),
                      col = dat$col, size = dat$lwd / 8, data = dat)
}
ggpoint <- function (dat)
{
    ggplot () + ggmin_theme () +
        geom_point (aes (x = x, y = y), col = dat$col, data = dat)
}
```
One set of random lines can then be generated and plotted via `ggplot2` like
this:
```{r fig}
dat <- getlines (n = 1e5, xylim = 1000)
ggline (dat)
```

The equivalent output of `svgplotr` can be directly viewed as a `.html`, or a
`.svg` file can be converted to any other format using the `rsvg` package:
```{r rsvg, eval = FALSE}
svgplot_lines (dat, file = "junk", html = FALSE) # makes junk.svg
require (rsvg)
png::writePNG (rsvg ("junk.svg"), "junk.png")
```
```{r imagemagick, echo = FALSE, eval = FALSE}
system2 ("convert", c ("junk.png", "-resize 1000x700!", "junk.png"))
junk <- file.remove ("junk.svg")
#system2 ("xdg-open", "junk.png &")
```
```{r png-via-knitr, out.width = "75%", echo = FALSE}
#knitr::include_graphics ("junk.png")
```


## Timing Comparison

`svgplotr` is considerably faster than `svglite`, but speed differences depend
on numbers of edges plotted. The following code quantifies the time
taken to plot both lines and points by `svglite` in comparison to `svgplotr` as
a function of `n`.
```{r timing, eval = FALSE}
require (svglite)
require (rbenchmark)
plotgg <- function (fig)
{
    svglite ("lines.svg")
    print (fig)
    graphics.off ()
}

testlines <- function (n = 1e3, nreps = 5)
{
    dat <- getlines (n = n)
    fig <- ggline (dat)
    benchmark (
               plotgg (fig),
               svgplot_lines (dat, filename = "lines"),
               order = "test",
               replications = nreps)$relative [1]
}

testpoints <- function (n = 1e3, nreps = 5)
{
    dat <- getpoints (n = n)
    fig <- ggpoint (dat)
    benchmark (
               plotgg (fig),
               svgplot_points (dat, filename = "lines"),
               order = "test",
               replications = nreps)$relative [1]
}

n <- 10 ^ (20:60 / 10)
ylines <- sapply (n, testlines)
ypoints <- sapply (n, testpoints)
dat <- data.frame (n = n, lines = ylines, points = ypoints)
```
```{r cleanup, echo = FALSE, eval = FALSE}
junk <- file.remove (c ("lines.html", "lines.svg"))
```{r, echo = FALSE, eval = FALSE}
# warning: with n -> 1e6, each takes ~ 10 minutes; # n -> 1e5 takes < 1 minute
system.time ( ylines <- sapply (n, testlines))
system.time ( ypoints <- sapply (n, testpoints))
save (dat, file = "timing-results.rda")
```
```{r, echo = FALSE}
load ("timing-results.rda")
```
Then plot the results
```{r plot-timings}
dat <- tidyr::gather (dat, key = "n")
names (dat) <- c ("n", "type", "y")
ggplot (dat, aes (x = n, y = y, group = type)) +
    theme (panel.grid.minor = element_blank ()) +
    scale_x_log10 (breaks = 10 ^ (2:6)) +
    scale_y_log10 (limits = c (1, max (dat$y)), breaks = c (1:5, 10, 50, 100)) +
    scale_colour_manual (values = c ("red", "blue")) +
    geom_point (aes (colour = type)) +
    geom_smooth (aes (colour = type), method = "loess", se = TRUE) +
    ylab ("time (svgplotr) / time (svglite)") +
    labs (title = "relative performance of svgplotr vs svglite")
```

And efficiency gains initially decrease exponentially, but then flatten out and
appear to approach asymptotic limits. Even for the maximum size in this plot of
1 million objects, `svgplotr` is almost 4 times faster than `svglite` for lines,
and over 8 times faster for points. The right portion of the graph may also be a
second exponential regime, but even if so, parity for lines is only going to be
reached at:
```{r}
indx <- which (dat$n >= 1e5 & dat$type == "lines")
mod <- as.numeric (lm (log10 (dat$y [indx]) ~ log10 (dat$n [indx]))$coefficients)
format (10 ^ (mod [1] / abs (mod [2])), scientific = TRUE, digits = 2)
```
which is 130 billion edges, and obviously enormously more for points. Parity is
not really going to happen, and `svgplotr` will always remain faster than
`svglite`.
