---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/mpadge/svgplotr.svg)](https://travis-ci.org/mpadge/svgplotr) 
[![Project Status: Concept - Minimal or no implementation has been done yet.](http://www.repostatus.org/badges/0.1.0/concept.svg)](http://www.repostatus.org/#concept)

# svgplotr

Fast `svg` plots in **R**. Currently just a demonstration of speed relative to
[`svglite`](https://github.com/r-lib/svglite). The function `getdat()` generates
a series of random edges with varying colours and line widths to be plotted.
Comparison is against a `ggplot2` object with no embellishments, set up with the
following code
```{r load, echo = FALSE, message = FALSE}
devtools::load_all (".", export_all = FALSE)
```
```{r ggplot-setup, message = FALSE}
require (ggplot2)
ggmin_theme <- function ()
{
    theme <- theme_minimal ()
    theme$panel.background <- element_rect (fill = "transparent",
                                                     size = 0)
    theme$line <- element_blank ()
    theme$axis.text <- element_blank ()
    theme$axis.title <- element_blank ()
    theme$plot.margin <- margin (rep (unit (0, 'null'), 4))
    theme$legend.position <- 'none'
    theme$axis.ticks.length <- unit (0, 'null')
    return (theme)
}
```
One set of random lines can then be generated and plotted like this:
```{r fig}
dat <- getdat (n = 1e4, xylim = 1000)
fig <- ggplot () + ggmin_theme () +
    geom_segment (aes (x = xfr, y = yfr, xend = xto, yend = yto,
                       colour = col, size = lwd), size = dat$lwd, data = dat)
print (fig)
```

## Timing Comparison

```{r timing}
require (svglite)
plotgg <- function (fig)
{
    svglite ("lines.svg")
    print (fig)
    graphics.off ()
}

rbenchmark::benchmark (
                       plotgg (fig),
                       svgplot (dat, filename = "lines"),
                       replications = 5) [, 1:5]
```
And `svgplotr` is close to an order of magnitude faster than `svglite`.
```{r cleanup, echo = FALSE}
junk <- file.remove (c ("lines.html", "lines.svg"))
```
